Quantum-assisted unsupervised data clustering

### 2020-05-07 manuscript.tex
Dehighlight Alexey comment #37

At this stage, the information regarding the differences between pairs of $\{X\}$ and $\{Y\}$ \hl{encoded in the amplitudes, in order to extract the Hamming distances between the relevant $\left| x_i \right\rangle$, $\left| y_j \right\rangle$ we return to our initial basis} for register $\left| X \right\rangle$ by applying pairwise CNOT gates:
%
\begin{multline}
	\label{eq:final_state}
    \left| \psi_f \right\rangle =  
    \frac{1}{\sqrt{kl}}\sum\limits_{i, j=1}^{k} 
	\left[ 
	    \cos\left(
	        \dfrac{\pi}{2n}
	        \sum\limits_{\alpha=1}^n d^{(\alpha)}_{ij} 
	    \right)
        \left| x_i \right\rangle 
        \left| y_j \right\rangle 
        \left| 0 \right\rangle\right.
        \\+
        \left. i \sin\left(
            \dfrac{\pi}{2n}
            \sum\limits_{\alpha=1}^n d^{(\alpha)}_{ij} 
        \right)
        \left| x_i \right\rangle 
        \left| y_j \right\rangle 
        \left| 1 \right\rangle
    \right] .
\end{multline}
%
This makes $\{X\}$ store the input vectors again, as in the initial step 
and preserves the amplitudes of the auxiliary qubit which are proportional to how different each pairs of $\{X\}$ and $\{Y\}$ are.

>>>>

At this stage, the information regarding the differences between pairs of $\{X\}$ and $\{Y\}$ encoded in the amplitudes, in order to extract the Hamming distances between the relevant $\left| x_i \right\rangle$, $\left| y_j \right\rangle$ we return to our initial basis for register $\left| X \right\rangle$ by applying pairwise CNOT gates:
%
\begin{multline}
	\label{eq:final_state}
    \left| \psi_f \right\rangle =  
    \frac{1}{\sqrt{kl}}\sum\limits_{i, j=1}^{k} 
	\left[ 
	    \cos\left(
	        \dfrac{\pi}{2n}
	        \sum\limits_{\alpha=1}^n d^{(\alpha)}_{ij} 
	    \right)
        \left| x_i \right\rangle 
        \left| y_j \right\rangle 
        \left| 0 \right\rangle\right.
        \\+
        \left. i \sin\left(
            \dfrac{\pi}{2n}
            \sum\limits_{\alpha=1}^n d^{(\alpha)}_{ij} 
        \right)
        \left| x_i \right\rangle 
        \left| y_j \right\rangle 
        \left| 1 \right\rangle
    \right] .
\end{multline}
%
This makes $\{X\}$ store the input vectors again, as in the initial step 
and preserves the amplitudes of the auxiliary qubit which are proportional to how different each pairs of $\{X\}$ and $\{Y\}$ are.
